A Switching Planner for Combined Task and Observation Planning

### 2010-11-29 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/evaluation.tex
I am stuck in Germany. Will be in Vienna at 9pm. Moritz, I will try to contact you then.

To test our approach we use a robot exploration domain based on a that
from our physical robotic system. Here, a robot is exploring an office
or living environment, and trying to report the locations of objects
to their owner.

@@

The robot can find out if an object is at a certain place by executing
the {\tt look-for-object} action. Moreover, the contents of a room
indicates its category, and certain objects are more likely to be
located in rooms of certain categories. For example, a box of
cornflakes is more likely to be located in the kitchen than the
office. The {\tt look-for-object} might result in a positive
perception if the object is there. Some objects are harder to detect
than others, and an instantaneous positive detection of the object is
not proof positive that it is there. Additionally, if the robot is in
the presence of a human, it can ask what type of room they are
currently in, however conducting a dialogue is more costly than
running a vision algorithm (cost of 8 vs costs of 3).

>>>>

To test our approach we use a robot exploration domain based on a
scenario from our physical robotic system. Here, a robot is
exploring an office or living environment, and trying to report the
locations of objects to their owner.

@@

The robot can find out if an object is at a certain place by executing
the {\tt look-for-object} action. Moreover, the contents of a room
indicates its category, and certain objects are more likely to be
located in rooms of certain categories. For example, a box of
cornflakes is more likely to be located in the kitchen than the
office. The {\tt look-for-object} might result in a positive
perception if the object is there. An instantaneous positive detection
of the object is not proof positive that it is there. Also, some
objects are harder to detect than others. Also, Additionally, if the
robot is in the presence of a human, it can ask what type of room they
are currently in, however conducting a dialogue is more costly than
running a vision algorithm (cost of 8 vs costs of 3).
